Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-08-23 2015-turklang-kazdep/paper.tex
better(?) bib fix?  Just turned off name disambiguation
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61534 72bbbca6-d526-0410-a7d9-f06f51895060
Acknowledgements
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61549 72bbbca6-d526-0410-a7d9-f06f51895060

%\usepackage{natbib}
%\bibdata{paper}
%\usepackage[backend=bibtex]{biblatex}
\usepackage[backend=biber,citestyle=apa,style=authoryear,maxbibnames=99,maxcitenames=2]{biblatex}
\bibliography{paper}
\renewcommand*{\nameyeardelim}{\addcomma\space}

@@

\emph{removed for review}

>>>>

%\usepackage{natbib}
%\bibdata{paper}
%\usepackage[backend=bibtex]{biblatex}
\usepackage[backend=biber,citestyle=apa,style=authoryear-comp,maxbibnames=99,maxcitenames=2,uniquename=false]{biblatex}
\bibliography{paper}
\renewcommand*{\nameyeardelim}{\addcomma\space}

@@

The authors would like to acknowledge Tolgonay Kubatova; Zhenisbek Assylbekov, Aida Sundetova, and colleagues; and Aibek Makazhanov for the various ways in which they each contributed to this research.
